
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on July 23rd, 2020, the consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported insufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was an Alternative Work Schedule (AWS) site. (IF PHONE CONFIRMATION: 

---

The Supervisor of Grounds, Luis Vasquez, reported that it does not have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter 1-2 times a day, including weekends. Staff begins collecting trash from 6:00 AM and ends at 4:30 PM daily. 

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, Red Hook East appeared in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

---

Red Hook East reported at the time of the interview that DSNY comes on Tuesdays, Wednesdays, and Saturdays. The consolidation also reported that it received 6 bulk tickets for the removal of bulk waste. The Supervisor of Grounds stated that 8 are needed a month. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 8 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management not to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using shoots. Waste is stored in the exterior compactor. 

The consolidation reported that on average, over 400 compactor bags (40 lbs. bags) are disposed of from Red Hook East daily. There are two exterior compactors at this consolidation.

According to the Compliance interview, there are no external sources of trash and bulk waste illegally dumped at this site. Luis Vasquez stated that more bulk tickets and staff are needed for the sprawling development.  

3. \textbf{Additional Context}

In a May 27th, 2020 report, the Monitor Cleanliness Team gave Red Hook East a B rating. 