
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on July 22nd, 2020, the consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported insufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was an Alternative Work Schedule (AWS) site. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement Based on the same summer of  2020 phone interview, the consolidation gave the following responses.

---

South Jamaica reported at the time of the interview that DSNY comes the following day when called. The consolidation also reported that it received 8 bulk tickets for the removal of bulk waste. The Superintendent stated more bulk containers are needed. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 14 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management not to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using shoots or nondesignated drop-off sites. Waste is stored in the exterior compactor. 

The consolidation reported that on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Íouth Jamaica daily. There are 4 exterior compactors at this consolidation.

South Jamaica reports that if necessary, it may receive trash from Baisley Park Houses. According to the Compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from unknown sources. 

3. \textbf{Additional Context} 

In a May 19th, 2020 report, the Monitor Cleanliness Team gave South Jamaica a C- rating. 