
\textbf{Inspection and Collection Requirement}s

The consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation gave the following responses.

The Supervisor of Grounds, Douglas Brevard, reported that East River does not have enough staff to correct observed deficiencies. Nonetheless, caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two to three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash around 6:30 AM and ends before 5:00 PM daily.



\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement. Based on the same summer of  2020 phone interview, the consolidation gave the following responses.



East River reported at the time of the interview that DSNY comes Tuesdays, Fridays, and Sundays. The consolidation also stated that it received nine bulk tickets for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at eighteen additional sites on the premises. After the trash is collected from the drop-off sites by the trucks, it is placed in an exterior compactor. Most tenants dispose of their trash using the trash chutes, but Mr. Brevard said there is still an abundance of garbage on the grounds. 



Mr. Brevard stated in the phone Interview that East River did not have a pest problem. The consolidation reported that, on average, less than 100 compactor bags (40 lbs. bags) are disposed of from East River daily. There are two exterior compactors at this consolidation; however, one was broken at that time.  Mr. Brevard stated that both compactors have holes in them and that he has reached out to Arrow Steel to do repairs. Mr. Brevard also noted Arrow Steel has told him that both compactors need to be replaced. 

East River reports that it does not take waste to any other neighboring developments nor accept others waste. According to the phone interview, there are external sources of trash, and bulk waste illegally dumped at this site. When illegal dumping occurs, it is usually from construction companies and locals. The biggest obstacle East River faces that in preventing a clean campus is construction being done throughout the development. According to Mr. Brevard, the best thing Management/Operations has done to improve waste management is to receive more bulk tickets.  

3. Additional Context

In a June 24, 2020 report, the Monitor Cleanliness Team gave East River a B-/C+ rating.