

1. \textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

---

The Property Manager, Ayodeji Festus, reported that Kingsborough does not have enough staff to correct observed deficiencies and caretakers can  usually complete all of their tasks in a day. NYCHA caretakers pick[ed] up trash inside the buildings as needed throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter as needed throughout the day, including weekends. Staff begins collecting trash between 6:00 AM and 6:45 PM daily. 

2. \textbf{Removal or Storage Requirement}

The consolidation did not appear to be in compliance with the removal or storage requirement of Paragraph 45 of the HUD Agreement because it does not have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of 2020 survey, the consolidation reported the following conditions.

---

Kingsborough reported at the time of the survey that DSNY comes Mondays, Wednesdays, Fridays, and Saturdays. The consolidation also reported that it received 6 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 8 additional sites on the premises. After the trash is collected from the drop-off sites, it is left at the drop-off site. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using shoots, in front of their buildings, or in front of hallway hopper doors. Once waste is collected from the grounds, waste is stored at drop-off sites for DSNY pickup..

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Kingsborough daily. There are no exterior compactors at this consolidation.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from construction companies. According to Mr. Festus, illegal dumping is an obstacle preventing caretakers from keeping Kingsborough free of trash and litter. .

3. \textbf{Additional Context}

In a June 9th, 2020 report, the Monitor Cleanliness Team gave Kingsborough a B/A- rating.