

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

---

The Housing Manager, Tedric Gamble, reported that Marcy does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings as needed throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter as needed throughout the day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

---

Marcy reported at the time of the survey that DSNY comes as needed. The consolidation also reported that it received 7 bulk tickets a month for the removal of bulk waste. The Housing Manager reported that the consolidation can use 8 tickets. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation do not have access to trash chutes and may drop their waste at 70 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash in front of their buildings. Once waste is collected from the grounds, waste is stored in the exterior compactor. 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Marcy daily. There are 3 exterior compactors at this consolidation.

Marcy reports that if necessary, it can take its trash to Tompkins or Whitman. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from construction and household bulk trash.Tedric Gamble stated that a lack of adequate staffing is preventing caretakers from keeping Marcy free of litter and trash. 

3. \textbf{Additional Context} 

In a May 27th, 2020 report, the Monitor Cleanliness Team gave Marcy a A/A- rating. 