
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on September 20, 2019, the Astoria Consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported sufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was not an Alternative Work Schedule (AWS) site. A follow up phone call to the site in the summer of 2020 confirmed that the development was checking the site and removing waste seven days a week.

The Supervisor of Grounds, Antoine Dickson, reported that Astoria does have enough staff to correct most observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings one to two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter one to two times a day, not including weekends thus they are not in compliance with Paragraph 45. Staff begins collecting trash between 8:00 AM -- 10:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, the Astoria appeared to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. At the time of the interview, Mr. Dickson reported a need for increased staffing that could contribute to ongoing pest problems. More follow up is since Astoria has become an AWS site.

Astoria reported at the time of the interview that DSNY is called for collection when the compactor is full. The consolidation also reported that it received three to four bulk tickets for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 23 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Waste is stored in exterior compactors. 

A single site visit on September 20, 2019 showed satisfactory conditions with lids covering all waste bins. It also showed that waste was not stored in a way that prevents pests on that day. Mr. Dickson stated in the Compliance Interview that Astoria did have a pest problem.

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Astoria daily. There are three exterior compactors at this consolidation. 

According to the Compliance Interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is mostly from passerby's. 

3. \textbf{Additional Context}

In a June 24, 2020 report, the Monitor Cleanliness Team gave Astoria a D rating.