 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Patrice Grace, reported that King Towers does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings frequently throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash around 6:00 AM and ends around 6:30 PM.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.  

The King Towers consolidation reported at the time of the survey that DSNY comes Tuesdays and Fridays. The consolidation also stated that it received eight bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in exterior compactors. Most tenants dispose of their trash using the trash chutes. Once the waste is collected from the grounds, it is stored in the exterior compactors.  

 

Ms. Grace stated in the survey that King Towers did have a pest problem, but exterminators are treating it. The consolidation reported that, on average, 110 compactor bags (40 lbs. bags)  are disposed of from King Towers daily. There are two exterior compactors at this consolidation that were both in good condition with no holes at the time of the survey. 

This consolidation does not take its waste to other developments nor accept garbage from other developments. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site.  Ms. Grace stated that the most significant obstacle King Towers faces regarding waste management is the residents. She also reported that the best thing Management/Operations has done for trash management was giving King Towers more bulk tickets for storage.

3. \textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Grampian Houses a C rating. King Towers has not yet been graded.