 

\textbf{Inspection and Collection Requirement} 

 

In a compliance interview conducted on November 26th, 2019, the Albany Consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. At the time of this interview, the site was an Alternative Work Schedule (AWS) site. 

--- 

The Supervisor of Grounds, Hector Irizzary, reported that Albany does not have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter 1-2 times a day, including weekends. Staff begins collecting trash after 10:00 AM and ends before 4:00 PM daily. 

 

\textbf{Removal or Storage Requirement} 

At the time of the compliance interview, Albany appeared to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste.

 

--- 

Albany reported at the time of the interview that DSNY comes on Mondays, Wednesdays, and Fridays. The consolidation also reported that it received 9 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at any additional sites on the premises. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using shoots. Once waste is collected from the grounds, waste is stored in the exterior compactor.  

 

A single site visit on November 26th, 2019 showed exposed trash on the curbside and development grounds, along with recycling bins placed throughout the site. There were no trash bins found on the site. It also showed that waste was not stored in a way that prevents pests on that day. Hector Irizzary stated in the compliance interview that Albany did not have a pest problem. 

 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) and 3-4 2 yard containers are disposed of from Albany daily. There are 3 exterior compactors at this consolidation.

 

According to the compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from construction companies.