Bronx River Analysis: 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Sunny Vellavallil, reported that the Bronx River consolidation does not have enough staff to correct observed deficiencies, and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings four times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 6:00 PM daily. 

\textbf{Removal or Storage Requirement} 

This site is at least partially curbside and is not in compliance with removal and storage requirement of Paragraph 45 of the HUD Agreement because on days when DSNY cannot pick up waste that is not stored in exterior compactors is not stored in a manner that prevents pests. The curbside development at this consolidation is Boynton Avenue Rehab. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

At the time of the survey, Bronx River reported that DSNY comes when the compactors are full, usually three times a week. The consolidation also stated that it received eight bulk tickets a month for the removal of bulk waste.  Bulk trash sits in a yard with an exterior container before being picked up by the vendor.  In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at additional sites on the premises. Most tenants dispose of their trash the trash chutes. Once the waste is collected from the grounds, it is stored in the exterior compactors. However, at Boynton Avenue it is stored in the compactor rooms in garbage bags. It is take outside two times a week by caretakers for pickup by sanitation.

 

In the survey, Mr. Vellavallil stated that the consolidation did have a pest problem, but that an exterminator is treating the problem. The consolidation reported that, on average, 70 compactor bags (40 lbs. bags)  are disposed of from Bronx River daily. There are three exterior compactors at this consolidation. 

Bronx River does not take it trash, nor accept waste from other developments. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Mr. Vellavallil stated that the most significant thing Management/Operations has done for waste management is to educate residents and post flyers throughout the building's lobbies.

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Bronx Houses a C+/D- rating.  Bronx River Addition and Boynton Avenue Rehab have not been graded at this time. 