Gun Hill Analysis: 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Dwarka Rupnarain, reported that the Gun Hill consolidation does not have enough staff to correct observed deficiencies because of AWS. However, caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 6:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the garbage. Based on the same summer of  2020 survey, the consolidation reported the following conditions. 

 

The Gun Hill consolidation reported at the time of the survey that DSNY comes two times a week. The consolidation also stated that it received four bulk tickets a month to remove bulk waste, but could sometimes use more. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at six additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactors. Most tenants dispose of their trash by leaving it in front of the buildings. Once the waste is collected from the grounds, it is stored in the compactors.  

 

The Superintendent stated in the survey that the consolidation did not have a pest problem. The consolidation reported that, on average, 60 compactor bags (40 lbs. bags) are disposed of from Gun Hill daily. There are two exterior compactors at this consolidation that were both in good condition with no holes at the time of the survey. 

Gun Hill reports that if necessary, it can take its trash to Eastchester Houses and Parkside House and also may receive trash from those developments. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is mostly sheetrock and wood debris.  The superintendent state the biggest obstacle Gun Hill faces regarding trash management is the AWS schedule. 

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Gun Hill houses an A rating.  