 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Supervisor of Caretakers, Charlie Stuckey, reported that the Dyckman consolidation does not have enough staff to correct observed deficiencies. However, caretakers can usually complete all of their tasks in a day, but not as thoroughly as they would like. NYCHA caretakers pick up trash inside the buildings frequently throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

  

Dyckman reported at the time of the survey that DSNY comes when the compactors are full, usually three to four days a week. The consolidation also stated that it received five bulk tickets a month to remove bulk waste but needs more to handle the volume of garbage. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at seven additional sites on the premises.  Most tenants dispose of their trash by using the trash chutes. Once the waste is collected from the grounds, it is stored in the exterior compactors.  

 

Mr. Stuckey stated in the survey that consolidation did not have a pest problem. The consolidation reported that, on average, 140 compactor bags (40 lbs. bags)  are disposed of from Dyckman daily. There are two exterior compactors at this consolidation that were in good condition with no holes at the time of the survey. 

Dyckman does not take its waste to, nor accept waste from, other developments. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site but are unsure of who is doing the dumping. Mr. Stuckey said the most important thing Management/Operations has done to improve trash management is to provide more bulk tickets.

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Dyckman Houses an A rating.  

 