 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Christopher Hague, reported that the Todt Hill consolidation does have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 8:15 AM and ends around 3:00 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of an exterior compactor to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

  

Todt Hill said at the time of the survey that DSNY comes twice a week, Mondays and Thursdays, and recycling is on Saturdays. The consolidation also stated that it received five to seven bulk tickets a month to remove bulk waste.  Bulk trash sits in a yard with an exterior container before being picked up by the vendor.  In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at additional sites on the premises. Most tenants dispose of their trash by using the trash chutes and leaving it in front of the buildings and by the waste compound. Once the waste is collected from the grounds, it is stored in the exterior compactor.  

 

Mr. Hague stated in the survey that consolidation did not have a pest problem. The consolidation reported that, on average, 75 to 90 compactor bags (40 lbs. bags)  are disposed of from Todt Hill daily. There is one exterior compactor at this consolidation that is only a few months old and in good condition. 

This consolidation does not bring its waste nor accept waste from other developments. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is usually bulk materials, but the consolidation has installed cameras and is working diligently with sanitation to hold dumpers accountable. According to Mr. Hague, the most significant obstacle Todt Hill faces regarding trash management is residents not disposing of trash properly, thus causing extra work for caretakers. He also stated that the best thing Management/Operations has done is work with Capital Projects to have a new exterior compactor and compound installed and put an end to curbside garbage bag pickups.  

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Todt Hill Houses a B rating.  

 