
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation gave the following responses.

---

The Superintendent, Ermal Mujovic, reported that it does not have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick[ed] up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conduct[ed] ground inspections and pick[ed] up litter 1-2 times a day, including weekends. Staff begins collecting trash between 8:00 AM -- 10:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD  Agreement Based on the same summer of  2020 phone interview, the consolidation gave the following responses.

---

Pomonok reported at the time of the interview that DSNY comes roughly 5 times a week. The consolidation also reported that it received 10 bulk tickets for the removal of bulk waste., although more is needed. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 24 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management not to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using the shoot system. Waste is stored in the exterior compactor. 

The consolidation reported that on average, 350-400 compactor bags (40 lbs. bags) are disposed of from Pomonok daily. There are 5 exterior compactors at this consolidation. 

According to the Compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from unknown sources. Ermal Mujovic states that there isn't enough staff all week due to AWS scheduling. 

3. \textbf{Additional Context} [optional -- if applies]

In a June 10th, 2020 report, the Monitor Cleanliness Team gave Pomonok a C rating. 