

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

The Assistant Property Maintenance Supervisor, Isamilly Montas, reported that Carver does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 4:30 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Carver reported at the time of the survey that DSNY comes when called for collection. The consolidation also reported that it received nine bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at additional sites on the premises. Most tenants dispose of their trash using trash chutes. Once waste is collected from the grounds, waste is stored in an exterior compactor. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Carver daily. There are three exterior compactors at this consolidation and two 30-yard bulk containers. Carver reported that two of the exterior compactors are out of order and the consolidation  is reaching out to Arrow Steel for repairs. Ms. Montas also reported that there are 13 interior compactors.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. The source of the illegal dumping is unknown. Ms. Montas reported no pests infestations, but a need for more staff to deal with waste at the site.