

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a questionnaire conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Mary Joseph, reported that Washington does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three times a day, including weekends. Staff begins collecting trash at 8:00 AM  and ends before 7:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement. Based on the same summer 2020 questionnaire, the consolidation reported the following conditions.

The Washington Consolidation reported at the time of the interview that DSNY comes every two days. The consolidation also reported that it does not participate in the bulk waste ticket program. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at additional sites on the premises located at the rear of the buildings. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash at drop-sites in the rear of the buildings. Waste is stored in exterior compactors. 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Washington daily. There are six exterior compactors at this consolidation. Ms. Joseph reported that there are 18 interior compactors which are all accessible. However, interior compactors in buildings 5, 6, 7 and 14 are shut down.

According to the questionnaire, there are no external sources of trash and bulk waste illegally dumped at this site. Ms. Joseph reported that the AWS schedule negatively impacts staffing. The consolidation also uses signs and strategic placement of trash bins for waste disposal. Daily extermination is applied to combat ongoing pest problems.

3. \textbf{Additional Context}

In a June 24, 2020 report, the Monitor Cleanliness Team gave Washington a B rating. 