

\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on November 26th, 2019, the Breevort Consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. At the time of this interview, the site was not an Alternative Work Schedule (AWS) site. 

---

The Supervisor of Caretakers, Tyreek Penn, reported that Breevort does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter 3-4 times a day, including weekends. Staff begins collecting trash after 10:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, Breevort did not appear to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does not have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

---

Breevort reported at the time of the interview that DSNY comes Tuesdays and Thursdays. The consolidation also reported that it received 5-6 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at any additional sites on the premises. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using shoots or in front of their buildings with no bins. Once waste is collected from the grounds, waste is stored in the exterior compactor. 

The consolidation reported that, on average, less than 100 compactor bags (40 lbs. bags) and over 8 2-yard containers are disposed of from Breevort daily. There are 2 exterior compactors at this consolidation, one of which has a hole in need of welding. Mr. Penn stated that he intended to reach out to contact Arrow Steel to weld the hole.

According to the compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from construction, restaurants, and passersby.The Supervisor of Caretakers stated that residents not cooperating and broken lobby doors which allow people to trespass are obstacles preventing caretakers from keeping Breevort free of trash and litter. 