Cooper Park Analysis: 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Maintenance Supervisor, Fia Cook, reported that the Cooper Park consolidation has enough staff to correct observed deficiencies. Caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash at 6:00 AM and ends at 3:45 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

  

Cooper Park reported at the time of the survey that DSNY comes on Wednesdays and Saturdays. The consolidation also stated that it received three to five bulk tickets a month to remove bulk waste.  Bulk trash sits in a yard with an exterior container before being picked up by the vendor.  In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at seven additional sites on the premises. Most tenants dispose of their trash by using the trash chutes. Once the waste is collected from the grounds, it is stored in the exterior compactors.  

Ms. Cook stated in the survey that Cooper Park did not have a pest problem. The consolidation reported that, on average, 80 compactor bags (40 lbs. bags)  are disposed of from Cooper Park daily.  There are two exterior compactors at this consolidation that were both in good condition at the time of the survey. 

Cooper Park does not take its waste to other developments nor accept garbage from other developments. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. 

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Cooper Park Houses an A rating.  