
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on December 3rd, 2019, the consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported sufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was an Alternative Work Schedule (AWS) site. 

---

The Supervisor of Grounds, Norman Buie, reported that it does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter 1-2 times a day, including weekends. Staff begins collecting trash between 6:00 AM -- 8:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, Howard appeared in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

---

Howard reported at the time of the interview that DSNY comes on Mondays and Fridays. The consolidation also reported that it received 3-4 bulk tickets for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation do not have access to trash chutes and may drop their waste at 11 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management not to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using drop-off sites, but usually may not place trash directly inside the trash bins. Waste is stored in the exterior compactor. 

A single site visit on December 3rd, 2019 showed exposed trash on the development grounds upon both arrival and departure. Trash bins were placed throughout the site with no lids. It also showed that waste was stored in a way that prevents pests on that day. Norman Buie stated in the Compliance Interview that Howard did not have a pest problem. 

The consolidation reported that on average, less than 100 compactor bags (40 lbs. bags) are disposed of from Howard daily. There are 2 exterior compactors at this consolidation.

Howard reports that if necessary, it can take its trash to Van Dyke and Tilden Houses and may receive trash from Hughes, Brownsville, and Tilden Houses. According to the Compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from medical offices and nearby restaurants. 