
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Supervisor of Housing Caretakers, Ronald Stokes, reported that Wagner does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Wagner reported at the time of the survey that DSNY comes when called for collection, which happens daily. The consolidation also reported that it received 15 bulk tickets a month for the removal of bulk waste. Mr. Stokes reports that Wagner always needs to request more tickets. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at additional sites in front of each building. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash in the hallways or using the drop-off sites. Once waste is collected from the grounds, waste is stored in an exterior compactor. 

The consolidation reported that, on average, 200-300 compactor bags (40 lbs. bags) are disposed of from Wagner daily. There are five exterior compactors and four 30-yard bulk containers at this consolidation. Mr. Stokes also reported that there are 22 interior compactors, all of which are accessible. 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site, but the source is unknown. Mr. Stokes reported that the consolidation needs more staff to deal with the constant disposal of waste. He also noted that Wagner would benefit from more bulk tickets and a bulk crusher.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Wagner a D rating. 