 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Sherrie Allen, reported that the Mariner's Harbor consolidation does not have enough staff to correct observed deficiencies. Caretakers can only complete all of their tasks when they are fully staffed. NYCHA caretakers pick up trash inside the buildings at least three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

  

Mariner's Harbor reported at the time of the survey that DSNY comes Mondays and Thursdays. The consolidation also stated that it received five bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 32 additional sites on the premises. After the trash is collected from the drop-off sites and grounds, it is placed in the exterior compactors. 

 

Ms. Allen stated in the survey that consolidation did not have a pest problem. The consolidation reported that, on average, 60 compactor bags (40 lbs. bags)  are disposed of from Mariner's Harbor daily. There are two exterior compactors at this consolidation that were in good condition at the time of the survey, 

Mariner's Harbor does not take its trash to other development nor accept other developments waste. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Ms. Allen said the best thing Management/Operations has done to improve trash management is to assign all staff when needed to assist with grounds to keep the development free of the trash. She also stated that residents could help more with keeping the ground cleaner and being more accountable. 


\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Mariner's Harbor an A- rating.  

 