 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions. 

The Property Manager, Zachary Husser, reported that the Highbridge Gardens consolidation does not have enough staff to correct observed deficiencies. However, caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings five times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 6:00 PM daily. 

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Highbridge Gardens reported at the time of the survey that DSNY comes Fridays. The consolidation also stated that it received, on average, eight bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at six additional sites on the premises. Most tenants dispose of their trash by using the trash chutes. Once the waste is collected from the grounds, it is stored in the exterior compactors.  

 

Mr. Husser stated in the survey that Highbridge Gardens did not have a pest problem. According to the Highbridge Gardens Rat Reduction Action Plan, as of June 2019, it continues to have a very low burrow count. Historically, it has not had more than four. The consolidation reported that, on average, 90 compactor bags (40 lbs. bags)  are disposed of from the consolidation daily. There are two exterior compactors at this consolidation that were all in good condition at the time of the survey. 

Highbridge Gardens does not take its trash to other developments, nor take waste from other developments. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. According to Ms. Husser, the most significant improvement Management/Operations has done regarding waste management is place signs where to place garbage.

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Highbridge Gardens an A rating.  