


\textbf{Inspection and Collection Requirement}s 

 

In a Compliance interview conducted on December 24, 2019, the Castle Hill Consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. The consolidation reported sufficient staff to meet the requirements. At the time of this interview, the site was an Alternative Work Schedule (AWS) site.

 

The Supervisor of Caretakers reported that Castle Hill consolidation does have enough staff to correct observed deficiencies, and caretakers  can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter at least three times a day. Staff begins collecting trash between 6:00 AM -- 8:00 AM and ends after 5:00 PM daily.



Removal or Storage Requirement 

 

At the time of the Compliance interview, the Castle Hill consolidation appeared to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up garbage. 

  

At the time of the interview, the Castle Hill consolidation reported that DSNY comes Tuesdays, Wednesdays, Thursdays, Fridays, and Saturdays. The consolidation also stated that it received over eight bulk tickets a month to remove bulk waste. The consolidation noted that it could use around 15 bulk tickets a month. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 17 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in exterior compactors. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash by leaving it inside bins at the drop-off sites. After waste is collected, it is stored in exterior compactors. 

 

The Supervisor stated in the Compliance interview that Castle Hill did not have a pest problem, but waste could not be stored to prevent pests.



The consolidation reported that, on average, 100 -- 200 compactor bags (40 lbs. bags)  are disposed of from Castle Hill daily. There are four exterior compactors at this consolidation that were all in good condition with no holes at the time of the interview.  



The consolidation reports that it does not take its waste to other development but may occasionally receive trash from Soto Mayor Houses. According to the Compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from stores and private houses. The waste usually consists of construction materials, food, furniture, and appliances. 



3. Additional Context 

The Monitor Cleanliness Team has not yet graded Castle Hill Houses.