

\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on September 19th, 2019, the consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported sufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was not an Alternative Work Schedule (AWS) site. 

---

The Superintendent, Timothy Cox, reported that it does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter 1-2 times a day, including weekends. Staff begins collecting trash between 8:00 AM -- 10:00 AM and ends before 4:00 PM daily. 

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, Marlboro appeared in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

---

Marlboro reported at the time of the interview that DSNY comes on Mondays, Tuesdays, Wednesdays, and Thursdays. The consolidation also reported that it received 10 bulk tickets for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 28 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using trash shoots and designated drop-off sites. Waste is stored in the exterior compactor. 

A single site visit on September 19th, 2019 showed little to no trash on the grounds, with trash and recycling bins placed throughout the area with open lids. It also showed that waste was not stored in a way that prevents pests on that day. Timothy Cox stated in the Compliance Interview that Marlboro did not have a pest problem 

The consolidation reported that on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Marlboro daily. There are four exterior compactors at this consolidation.  

An obstacle facing staff at Marlboro is residents throwing trash out of windows. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Marlboro an A rating. 