

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Nakia McCoy, reported that Bushwick does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at  4:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Bushwick reported at the time of the survey that DSNY comes Mondays, Wednesdays, Fridays and Saturdays. The consolidation also reported that it does not received bulk tickets for the removal of bulk waste. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at additional sites on the premises. Tenants are  asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash outside of their buildings. Once waste is collected from the grounds, waste is stored in exterior compactors. 

The consolidation reported that, on average, 200-300 compactor bags (40 lbs. bags)  are disposed of from Bushwick daily. There are two exterior compactors and nine interior compactors at this consolidation. All of the compactors were accessible and functioning at the time of the survey

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. The source is unknown, but it usually comes in the form of bulk waste. Ms. McCoy reports that the consolidation is short staffed and requires more truck drives to remove litter from the ground. The consolidation was in the process of installing rodent-proof metal cages to store garbage cans at the time of the survey.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Bushwick a B/B- rating. 