

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

---

The Property Manager, Anjannette McInnis, reported that Baisley Park does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings 2 times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter 1-2 times a day, including weekends. Staff begins collecting trash at 8:30 AM and ends at 7:00 PM daily. 

\textbf{Removal or Storage Requirement}

This site is at least partially curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.

Curbside developments at this consolidation include the FHA Repossessed Houses.

---

Baisley Park reported at the time of the survey that DSNY comes on Saturdays. The consolidation also reported that it received 4-6 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 8 additional sites on the premises, located at the rear of each building. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using shoots. Once waste is collected from the grounds, waste is stored in the exterior compactor. 

The consolidation reported that, on average, 70 compactor bags (40 lbs. bags) are disposed of from Baisley Park daily. There are 3 exterior compactors at this consolidation 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from private contractors.