

\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on November 19, 2019, the Linden Consolidation did not appear to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported insufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was not an Alternative Work Schedule (AWS) site. The consolidation could not be reached for a follow up interview at this time to verify if implementation of AWS has allowed the to become compliant. 

The Supervisor of Grounds, Eric Matthew, reported that Linden does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings one to two times a day, not including weekends and thus they were not in compliance. NYCHA caretakers also conducted ground inspections and picked up litter one to two times a day, including weekends. Staff begins collecting trash between 8:00 AM -- 10:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, the Linden Consolidation appeared to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

Linden reported at the time of the interview that DSNY comes Mondays, Wednesdays and Fridays. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at three additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using the trash chutes. Waste is stored in exterior compactors.

A single site visit on November 19, 2019 showed satisfactory conditions by the end of the day, however, some trash and recycling bins did not have lids on them. It also showed that waste was stored in a way that prevents pests on that day. Mr. Matthew stated in the compliance interview that Linden did have a pest problem.

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Linden daily. There are four exterior compactors at this consolidation with at least one that has a hole in it . Mr. Matthew stated that he intended to reach out to contact either Arrow Steel or NYCHA to weld the hole.

Linden reports that if necessary, it can take its trash to Bay View Houses and vice versa. According to the compliance/phone interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is mostly from passerby's. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Linden an A rating. 