Taft Analysis: 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Assistant Property Supervisor, Guarionex Garcia, reported that the Taft consolidation does not have enough staff to correct observed deficiencies. Caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings frequently throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

 

Taft reported at the time of the survey that DSNY comes when the exterior compactors are full, usually three times a week. The consolidation also stated that it received 14 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at ten additional sites on the premises.  Most tenants dispose of their trash by using the trash chutes, but some throw it out the windows or leave it on the roof; or in the stairhalls and elevators. Once the waste is collected from the grounds, it is stored in the exterior compactors.

 

In the survey, Mr. Garcia stated that consolidation did have a pest problem in some buildings due to ongoing construction. Still, the contractor and NYCHA exterminator have been taking care of the issue. The consolidation reported that, on average, 140 compactor bags (40 lbs. bags)  are disposed of from Taft daily. There are four exterior compactors at this consolidation.

Taft does not take its waste to, nor accept waste from, other developments. According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. Mr. Garcia stated the most significant obstacles Taft faces regarding waste management are improper disposal by tenants, being short-staffed, and AWS.  He also said the most important things Management/Operations has done to improve trash management is to provide more bulk tickets.

 