
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Supervisor of Caretakers, Jorge Vargas, reported that the Lehman Village consolidation does have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. However, Lehman Village could use more manpower. NYCHA caretakers pick up trash inside the buildings two times a day, seven days a week. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash between 10:30 AM -- 11:30 AM and ends around 4:50 -- 6:45 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up garbage. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Lehman Village reported at the time of the survey that DSNY comes when the compactors are full, usually once a week. The consolidation also stated that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at four additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in exterior compactors. Most tenants dispose of their trash near the exits of the hallways. Once the waste is collected from the grounds, waste is stored in exterior compactors and bulk containers.  

Mr. Vargas stated in the survey that Lehman Village did have a pest problem, but that exterminators are handling the situation. The consolidation reported that, on average, 68 compactor bags (40 lbs. bags) are disposed of from Lehman Village daily. There are two exterior compactors at this consolidation that were in good condition with no holes at the time of the survey. 

This consolidation does not bring its waste to other developments, nor accept others waste. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Mr. Vargas said the biggest obstacle Lehman Village faces in terms of waste management is tenants disposing of garbage where they are not supposed to. He also stated that the most significant change Management/Operations has done to improve trash management at this consolidation is to put signs and notices letting tenants know where to dispose of trash and communicating with the TA president of the development.