
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in an online questionnaire conducted in the summer of 2020, the consolidation reported the following conditions.

The Supervisor of Grounds, Vincent J Valentino, reported that West Brighton does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 8:30 AM and ends at 7:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 questionnaire, the consolidation reported the following conditions.

West Brighton reported at the time of the questionnaire that DSNY comes Tuesdays and Thursdays. The consolidation also reported that it received five bulk tickets a month for the removal of bulk waste. Mr. Valentino reports that they always request more bulk tickets. Bulk trash sits in the compound before off-site removal. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at ten additional sites on the premises.  Tenants are asked by management to leave their garbage at designated sites on the grounds if they choose not to use the chutes. Mr. Valentino reports that tenants dispose of their trash in various places throughout the consolidation, including areas they shouldn't. Waste is stored in exterior compactors. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) and one 2-yard containers are disposed of from West Brighton daily. There are two exterior compactors at this consolidation. Mr. Valentino reports that they are over 20 years old and breakdown often. There are eight interior compactors that are all functioning at the time of the questionnaire.

 

According to the  questionnaire, there used to be issues with illegal dumping, but this has since been dealt with. Obstacles facing West Brighton include the AWS schedule, which Mr. Valentino notes is not working for his staff.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave West Brighton a D+ rating for storage and C+ rating overall.  