
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Kamal Hossain, reported that Richmond Terrace does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three to four times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three to four times a day, including weekends. Staff begins collecting trash at 8:00 AM and ends at 6:00 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Richmond Terrace reported at the time of the survey that DSNY comes when called for collection. The consolidation also reported that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Despite this, most tenants dispose of their trash on the curbside. Once waste is collected from the grounds, waste is stored in an exterior compactor. 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Richmond Terrace daily. There are three exterior compactors and two 30-yard bulk containers at this consolidation. Mr. Hossain also reported that there are ten interior compactors, all of which are operational.  

According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Mr. Hossain notes that resident compliance with waste disposal is an issue facing the consolidation. Occasional pest issues are dealt with by following NYCHA protocols. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Richmond Terrace a C+ rating. 