

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a questionnaire conducted in the summer of 2020, the consolidation reported the following conditions.

The Supervisor of Housing Caretakers, Bernard Williams, reported that Clinton does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three to four times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three to four times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 6:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 questionnaire, the consolidation reported the following conditions.

Clinton reported at the time of the survey that DSNY comes when called for collection. The consolidation also reported that it received five bulk tickets a month for the removal of bulk waste. Bulk trash sits in a fenced-in yard before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at three additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using trash chutes. Once waste is collected from the grounds, waste is stored in exterior compactors. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags)  are disposed of from Clinton daily. There are two exterior compactors and one 30-yard bulk container at this consolidation. Mr. Williams also reported that there are six interior compactors with one being heavily infested by rodents.

 According to the questionnaire, there are external sources of trash and bulk waste illegally dumped at this site. The source of the illegal dumping is unknown, but it mostly comes in the form of bulk waste. Obstacles facing the Clinton Consolidation surround residents not disposing of their waste in the proper areas.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Clinton a B rating. 