

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Latoya Hansley, reported that Wise Towers does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends before 4:00 PM daily.

\textbf{Removal or Storage Requirement}

All of the developments at this consolidation have their waste collected from the curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.

Wise Towers reported at the time of the survey that DSNY comes Tuesdays, Thursdays and Saturdays. The consolidation also reported that it received eight bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of the high rises in this development have access to trash chutes and may drop their waste at nine additional sites. There are 37 drop-off sites for the brownstones of the consolidation. Once waste is collected from the grounds, waste is brought to the curbside for collection by DSNY. 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Wise Towers daily. There are two 30-yard bulk containers and nine interior compactors, all of which are accessible. 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. Ms. Hansley reports that the source is mainly bulk waste in the form of appliances. She also reports pest problems at the brownstones, where weekly exterminations are taking place to mitigate the issue. 