
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Patrick Chan, reported that the Fulton consolidation does not have enough staff to correct observed deficiencies, and caretakers can only sometimes complete all of their tasks in a day, depending on staff attendance. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash around 6:00 AM and ends at 4:10 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Fulton reported at the time of the survey that DSNY comes when the compactor is full, usually three times a week. The consolidation also stated that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at two additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in exterior compactors. Most tenants dispose of their trash by leaving it outside of the buildings near the rear exits. Once the waste is collected from the grounds, waste is stored in the exterior compactors. 

In the survey, Mr. Chan stated that the Fulton consolidation did have a pest problem but that an exterminator regularly comes to treat the infestation. The consolidation reported that, on average, 28 compactor bags (40 lbs. bags) are disposed of from Fulton daily. There are two exterior compactors at this consolidation that are both in good condition. 

The Fulton consolidation does not bring its waste to other developments, nor accept garbage from other developments. According to the survey, there no external sources of trash and bulk waste illegally dumped at this site. Mr. Chan stated that the best thing Management/Operations has done for trash management has been to enforce illegal garbage disposal and educate residents about illegal garbage disposal. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Fulton Houses a B/B- rating. 