 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions. 

The Property Manager, Aida George, reported that the Issacs consolidation does not have enough staff to correct observed deficiencies. Still, caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. Staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily. 

 

\textbf{Removal or Storage Requirement} 

This site is at least partially curbside, and because DSNY does not pick up from the curb every day, there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up. The curbside development at this consolidation include is Robbins Plaza. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

 

The Issacs consolidation reported at the time of the survey that DSNY comes Mondays and Thursdays. The consolidation also stated that it received six bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at additional sites on the premises. Most tenants dispose of their trash by using the trash chutes. Once the waste is collected from the grounds at Issacs Houses and Holmes Tower, it is stored in the exterior compactors.  Since Robbins Plaza is a curbside site, more follow-up is needed to determine if this development stores its waste in a manner that prevents pests. 

 

The Property Manager stated in the survey that Issacs did not have a pest problem.  The consolidation reported that, on average, 100 -- 125 compactor bags (40 lbs. bags) are disposed of from Issacs daily. There is one exterior compactor at this consolidation that was in good condition with no holes at the time of the survey.

Issacs reports that if necessary, it can take its trash to Washington/Lexington Houses and Carver Houses and may receive trash from developments. According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. The most significant thing Management/Operations has done for Isaacs regarding trash management is place signs about proper waste disposal at the hopper doors, hallways, and lobbies.