 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Fernando Manso, reported that the Polo Grounds Towers consolidation does not have enough staff to correct observed deficiencies, and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings a minimum of five times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 6:30 PM daily.

\textbf{Removal or Storage Requirement} 

The consolidation appeared to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  survey, the consolidation reported the following conditions.

  

Polo Grounds Towers reported at the time of the survey that DSNY comes six times per week. The consolidation also stated that it received 13 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at four additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactors.  Most tenants dispose of their trash by throwing it out the windows or leaving it in front of the buildings. Once the waste is collected from the grounds, it is stored in the exterior compactors.  

 

Mr. Manso stated in the survey that the consolidation did have a pest problem. The IPM unit is currently inspecting and in the process of filling holes. Rodent proof door sweeps were installed to minimize points of entry.  There are three exterior compactors at this consolidation that were in good condition with no holes at the time of the survey.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is construction materials such as wood, tiles, and sheetrock. However, there are no cameras to determine who is doing the dumping. Mr. Manso said the most significant obstacle Polo Grounds Towers faces regarding waste management is being short-staffed. He also stated the best thing Management/Operations has done for trash management is to increase the number of bulk tickets.

\textbf{Additional Context} 

 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Polo Grounds Towers a B-/C+ rating.  

 