 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD Agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

The Housing Manager, Mildred Aviles, reported that the Straus consolidation does have enough staff to correct observed deficiencies, and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter at least twice daily. The staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily. 

\textbf{Removal or Storage Requirement} 

The consolidation did not appear to be in compliance with the removal or storage requirement of Paragraph  45 of the HUD Agreement because it does not have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up the waste. Based on the same summer of  2020  phone interview, the consolidation reported the following conditions.

  

Straus reported at the time of the interview that DSNY comes Mondays, Wednesdays, and Fridays. Straus does not receive bulk tickets because there is not enough space for a container. However, DSNY picks up the bulk on the days that it picks up the garbage. Bulk trash sits in a gated area with the other waste. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at three additional sites on the premises. Most tenants dispose of their trash by using the trash chutes. Once the waste is collected from the grounds, it is stored in a gated area in trash/compactor bags. On days when DSNY is going to pick up garbage, it is moved to the street.

Ms. Aviles stated in the interview that consolidation did not have a pest problem. One side of the consolidation did because of street food vendors, but there is now a regular rotation for extermination. The consolidation reported that, on average, 40 -- 45 compactor bags (40 lbs. bags)  are disposed of from Straus daily.

Straus reports that it does not take its waste to, nor accept waste from, any other developments. According to the interview, there are no external sources of trash and bulk waste illegally dumped at this site. Ms. Aviles said the most significant obstacle Straus faces regarding waste management is NYPD not responding to loitering complaints. The COVID-19 pandemic has exacerbated the situation. She also stated the best thing Management/Operations has done for trash management is to get DSNY to pick up the bulk waste.

\textbf{Additional Context}  

In a June 24, 2020 report, the Monitor Cleanliness Team gave Straus Houses and 344 East 28th Street A ratings. 