 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

 

--- 

The Property Manager, Tiffany Deputy, reported that Reid does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings as needed throughout the day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter as needed throughout the day, including weekends. Staff begins collecting trash between 8:30 AM and 4:00 PM daily. 

 

\textbf{Removal or Storage Requirement} 

 

This site is curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.

 

 

 

--- 

Reid reported at the time of the survey that DSNY comes on various days throughout the week according to the development. The consolidation also reported that it received 7 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 20 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed at the curbside for DSNY pickup. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using trash shoots. Once waste is collected from the grounds, waste is stored at the curb.  

 

 

The consolidation reported that, on average, 100-200 compactor bags (40 lbs. bags) are disposed of from Reid daily. There are no exterior compactors at this consolidation. Tiffany Deputy stated that a compactor is needed for this consolidation.  

 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from unknown sources. The Property Manager stated that residents are what's preventing caretakers from keeping Reid free of trash and litter. 

 