

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Michelle McGill-Felix, reported that the Langston Hughes Apartments does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 8:30 AM and ends between 3:30 PM -- 5:00 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Langston Hughes Apts reported at the time of the survey that DSNY comes Tuesdays and Thursdays. The consolidation also reported that it received three bulk tickets a month for the removal of bulk waste. Occasionally, more bulk tickets are needed. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation may drop their waste at two additional sites on the premises. Ms. McGill-Felix reported waste stored at the drop-sites are vulnerable to pests before being containerized. Most tenants dispose of their trash outside of their buildings. Once waste is collected from the grounds, waste is stored in an external compactor. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Langston Hughes daily. There is one exterior compactors at this consolidation and one 30-yard bulk container. Ms. McGill-Felix reported that the consolidation also has three interior compactors, which are all accessible.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. While the source is unknown, the illegal dumping consists mostly of bulk waste such as construction material and old furniture. Ms. McGill-Felix reports that the main obstacles facing her team include residents disposing of trash in incorrect areas such as out their windows and understaffing due to the new AWS system. She also stated that the creation of a Compactor Team and an additional Caretaker X has made a difference in waste management.