 

\textbf{Inspection and Collection Requirement} 

 

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

--- 

The Property Manager, George Johnson, reported that Low does not have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings 3 times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter 3 times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends before 4:00 PM daily. 

 

\textbf{Removal or Storage Requirement} 

The consolidation did not appear to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it does not have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste.Based on the same summer of  2020 survey, the consolidation reported the following conditions. 

 

--- 

Low reported at the time of the survey that DSNY comes on Mondays, Wednesdays, and Fridays. The consolidation also reported that it received 2 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 4 additional sites on the premises. After the trash is collected from the drop-off sites, it stays there until pickup by DSNY. Tenants are not asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash at the entrance of their buildings. Once waste is collected from the grounds, waste is stored at drop-off sites.  

 

The consolidation reported that, on average, less than 100 compactor bags (40 lbs. bags) are disposed of from Low daily. There are no exterior compactors at this consolidation.

 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from unknown sources. Residents not disposing of trash as instructed, illegal dumping, and the lack of exterior compactors are obstacles preventing caretakers from keeping Low free of litter and trash. 

  