O'
\textbf{Inspection and Collection Requirement}

The consolidation [APPEARED/DID NOT APPEAR] to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Assistant Property Maintenance Superintendent, Robert Craigwell, reported that O'Dwyer does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 6:15 AM and ends at 6:15 PM daily. 

\textbf{Removal or Storage Requirement}

(Option 1: The consolidation [APPEARED/DID NOT APPEAR] to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it [HAS/ DOES NOT HAVE] containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. [ADDITIONAL INFORMATION, IF APPLIES]). Based on the same summer of  2020 [phone interview or survey], the consolidation reported the following conditions.)

OR 

(Option 1.B Compliance was not able to do a site visit nor was a phone interview able to be conducted.)

OR

(Option 2: At the time of the compliance interview, the [CONSOLIDATION] [APPEARED/ DID NOT APPEAR] to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it [HAS/ DOES NOT HAVE] containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. [ADDITIONAL INFORMATION, IF APPLIES])

OR 

(Option 3: This site is [AT LEAST PARTIALLY] curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.) 

(3.a [IF PARTIALLY CURBSIDE] Curbside developments at this consolidation include [], [], and [].)

---

O'Dwyer reported at the time of the survey that DSNY comes three times a week. The consolidation also reported that it received eight bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at  additional sites on the premises. Most tenants dispose of their trash at designated drop-off sites. Once waste is collected from the grounds, waste is placed in a compound area before collection by DSNY

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from O'Dwyer daily. There are two 30-yard bulk  

(IF TRANSFER: [CONSOLIDATION] reports that if necessary, it can take its trash to [OTHER DEV(S)] and may receive trash from [OTHER DEVS.]) According to the [compliance/phone interview or survey], there [ARE/ARE NO] external sources of trash and bulk waste illegally dumped at this site. (IF DUMPING: When it happens, it is from [SOURCE].) (IF OBSTACLES AND IF PRIMARY IMPROVEMENTS: [SUPERVISOR] [REFER TO CELLS]. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave [CONSOLIDATION] a [GRADE] rating. 

*make note if there are not enough tickets ``At the time of interview the consolidation noted needing more tickets. Further inquiry is needed to verify that this is still the case.''

**if curbside state that there is more follow up necessary and conditions causing necessity of curbside (ie turnkey devs)

Consider Column BR in Phase 2 when there are no site visits in regards to consolidation compliance!!

Smartsheet