
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on July 20th, 2020, the consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. The consolidation reported sufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was an Alternative Work Schedule (AWS) site. 

---

The [POSITION], James Johnson, reported that it does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings 1-2 times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter 1-2 times a day, including weekends. Staff begins collecting trash between 9:00 AM and ends around 2:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement Based on the same summer of  2020 phone interview, the consolidation gave the following responses.

---

Woodson reported at the time of the interview that DSNY comes when needed. The consolidation also reported that it received no bulk tickets for the removal of bulk waste due to the fact that they have a bulk crusher on the site. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 3 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in the exterior compactor. Tenants are asked by management not to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using the shoot system. Waste is stored in the exterior compactor. 