
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Chemparathil Thomas, reported that Latimer Gardens does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 8:30 AM and ends at 5:00 PM daily. 

\textbf{Removal or Storage Requirement}

This consolidation partially has its waste collected from the curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up. The Bland Houses is the only development without access to an exterior compactor.

Latimer Gardens reported at the time of the survey that DSNY comes Mondays and Thursdays. The consolidation also reported that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at nine additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Most tenants dispose of their trash using trash chutes. Once waste is collected from the grounds, waste is stored in an exterior compactor or brought to the curbside. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Latimer Gardens daily. There is one exterior compactors at this consolidation and two 30-yard bulk containers. There are ten interior compactors, which are all accessible.

According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Latimer Gardens an A rating. 