Penn-:

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Jia Feng Wu, reported that Penn-Wortman does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash at 8:00 AM and ends at 2:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because one development has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. The other development does not have an exterior compactor, but contains waste in a basket inside a compactor room. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Penn-Wortman reported at the time of the survey that DSNY comes when called for collection, usually two times a week. The consolidation also reported that it received 4 bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at two additional sites on the premises. Tenants are asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Once waste is collected from the grounds, waste is stored in an exterior compactor or inside baskets in a compactor room depending on the development. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Penn-Wortman daily. There is one exterior compactor and one 30-yard bulk container at this consolidation. Ms. Wu also reports that there are four interior compactors, which are all accessible.

According to the survey, there are no external sources of trash or bulk waste illegally dumped at this site. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Penn-Wortman a B+ rating. 