
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Michael Lawrence, reported that Stuyvesant Gardens does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three times a day, including weekends. Staff begins collecting trash at 6:00 AM  and ends at 3:30 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Stuyvesant Gardens reported at the time of the survey that DSNY comes Tuesdays for collection. The consolidation also reported that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at four additional sites on the premises.  Most tenants dispose of their trash at the drop-off areas behind their buildings. Once waste is collected from the grounds, waste is stored in an exterior compactor.

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Stuyvesant Gardens daily. There is one exterior compactor and one 30-yard bulk container at this consolidation. Mr. Lawrence reports that there is also one interior compactor, which is accessible.

According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Pest problems are dealt with through weekly exterminations and filling of holes where pests could travel through.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Stuyvesant Gardens an A-/A rating. 