Taylor St --
\textbf{Inspection and Collection Requirement}

In a compliance interview conducted on October 1, 2019, the Taylor St -- Wythe Ave Consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. However, the consolidation reported insufficient staff to meet the collection portion of the requirements. At the time of this interview, the site was not an Alternative Work Schedule (AWS) site. 

The Supervisor of Grounds, Dominique Fields, reported that Taylor St -- Wythe Ave does not have enough staff to correct observed deficiencies , but caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings one to two times a day, including weekends. NYCHA caretakers also conducted ground inspections and picked up litter one to two times a day, including weekends. Staff begins collecting trash between 8:00 AM -- 10:00 AM and ends between 4:00 PM - 5:00 PM daily. 

\textbf{Removal or Storage Requirement}

At the time of the compliance interview, the Taylor St -- Wythe Ave Consolidation appeared to be in compliance with the storage and removal requirement of Paragraph 45 of the HUD Agreement because it does have containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. 

Taylor St -- Wythe Ave reported at the time of the interview that DSNY comes Tuesdays, Thursdays and Saturdays. The consolidation also reported that it received three to four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 14 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in an exterior compactor. Tenants are asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash at the drop-off site, but not in the bins. Waste is stored in front of each building before off site removal. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Taylor St -- Wythe Ave daily. There are two exterior compactors at this consolidation.

According to the compliance interview, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is mostly from passerby's. Ms. Fields reports that the biggest obstacle to better waste management is insufficient grounds staff.