

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a questionnaire conducted in the summer of 2020, the consolidation reported the following conditions.

 The Property Manager, Hector Hernandez, reported that Jackie Robinson does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers picked up trash inside the buildings six times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter six times a day, including weekends. Staff begins collecting trash around 8:30 AM and ends around 1:30 PM daily.

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come. Based on the same summer of  2020 questionnaire, the consolidation reported the following conditions.

Jackie Robinson reported at the time of the interview that DSNY comes when called for collection. The consolidation also reported that it received four to six bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may not drop their waste at additional sites on the premises. Tenants are not asked by management to leave their garbage on development grounds if they choose not to use the chutes. Most tenants dispose of their trash using trash chutes or in the parking lot. Waste is stored in interior compactors. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) and one 2-yard containers are disposed of from Jackie Robinson daily. There are two exterior compactors at this consolidation that have been recently repaired. 

 According to the questionnaire, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from various sources. Mr. Hernandez reports that obstacles preventing the consolidation from better waste management are the disruption of the AWS schedule and residents who do not use the trash chutes to dispose of waste.