
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Maintenance Supervisor, Alexis Nieves, reported that Marcus Garvey does not have enough staff to correct observed deficiencies and caretakers cannot always complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily.

\textbf{Removal or Storage Requirement}

Both of the developments at this consolidation have their waste collected from the curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.

Marcus Garvey reported at the time of the survey that DSNY comes Mondays, Wednesdays and Fridays. The consolidation also reported that it received four bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at five additional sites on the premises. Most tenants dispose of their trash using the trash chutes. Once waste is collected from the grounds, it is placed on the curbside for collection. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Marcus Garvey daily. There are two 30-yard containers and seven interior compactors, all of which are accessible. 

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from nearby homeowners and passerby's. Although Ms. Nieves reports no pest issues at present, management has requested for more frequent pickups of curbside waste. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Marcus Garvey an A-/B+ rating. 