
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Travis Abrams, reported that Claremont does not have enough staff to correct observed deficiencies, but caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct[ed] ground inspections and pick[ed] up litter two times a day, including weekends. Staff begins collecting trash at 8:00 AM and ends after 4:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Claremont reported at the time of the survey that DSNY comes when called for collection. The consolidation also reported that it received six bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 26 additional sites on the premises. After the trash is collected from the drop-off sites, it is placed in front of buildings for collection by grounds staff. Tenants are asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash using trash chutes. Once waste is collected from the grounds, waste is stored in exterior compactors. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Claremont daily. There are two exterior compactors and two 30-yard bulk waste containers at this consolidation. Mr. Abrams also reports that there are 26 interior compactors, which are all accessible.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. When it happens, it is from neighboring buildings and restaurants dumping their trash on NYCHA grounds. Mr. Abrams reports that the illegal dumping is one of the main obstacles towards better waste management along with the need for more staff. Pest problems are addressed regularly by internal exterminators and vendors.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave the Claremont Consolidation an A rating. 