Kraus Management (BX 3):

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Assistant Property Manager, Fausto Gudino, reported that Kraus Management (BX 3) does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings multiple times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter multiple times a day, including weekends. Staff begins collecting trash at 8:00 AM and ends at 4:30 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it stores waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Mr. Gudino reported that waste is stored in compactor rooms, however, more follow up is needed to ensure that the consolidation is in compliance with the storage requirement. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Kraus Management (BX 3) reported at the time of the survey that DSNY comes Mondays, Wednesdays, Fridays and Saturdays. The consolidation also reported that it does not use bulk tickets. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at additional sites on the premises. Most tenants dispose of their trash using trash chutes. Once waste is collected from the grounds, waste is stored in the compactor rooms before collection. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Kraus Management (BX 3) daily. There are ten interior compactors, three of which are not functioning properly. 

According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Mr. Gudino reports that there are pest issues, but Kraus Pest Control services the consolidation on a monthly basis or more often, if needed. He also noted that the DSNY collection schedule should be more efficient. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Kraus Management (BX 3) a B rating. 