

\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Tamisha Walters, reported that Union Avenue does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings three times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter three times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 4:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Union Avenue reported at the time of the survey that DSNY comes Tuesdays and Thursdays. The consolidation also reported that it received three bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, some residents of this consolidation have access to trash chutes and may drop their waste at additional sites on the premises. Most tenants dispose of their trash inside or in front of the buildings. Once waste is collected from the grounds, waste is stored in an exterior compactor. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Union Avenue daily. There are three exterior compactors and three 30-yard bulk containers at this consolidation. Ms. Walters also reported that there are three interior compactors, which are all accessible.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. Ms. Williams reported that staffing remains an obstacle to better waste management. The consolidation takes advantage of regular treatment to deal with pest problems.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Union Avenue an A rating. 