
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Superintendent, Cleveland Dunn, reported that Park Rock does not have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings once a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter once a day, including weekends. Staff begins collecting trash at 9:00 AM and ends before 4:00 PM daily. 

\textbf{Removal or Storage Requirement}

The developments at this consolidation have their waste collected from the curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up.

Park Rock reported at the time of the survey that DSNY comes Mondays, Wednesdays and Fridays. The consolidation also reported that it received three bulk tickets a month for the removal of bulk waste. Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at multiple drop-off sites. Most tenants dispose of their trash at the drop sites. Once waste is collected from the grounds, waste is placed on the curbside for collection by DSNY. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Park Rock daily. There is one 30-yard bulk container and 77 interior compactors, 11 of which are shutdown.

According to the survey, there are external sources of trash and bulk waste illegally dumped at this site. While the source is unknown, the illegal dumping consists mostly of bulk waste. Mr. Dunn reports that there are pest problems that are met with consistent extermination. Management has also requested that DSNY conducts more frequent pickups. 