Kraus Management (MB 1)
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a survey conducted in the summer of 2020, the consolidation reported the following conditions.

The Property Manager, Joy Lemon, reported that Kraus Management (MB 1) does have enough staff to correct observed deficiencies and caretakers can usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings two times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter two times a day, including weekends. Staff begins collecting trash between 8:00 AM -- 9:00 AM and ends before 3:30 PM daily. 

\textbf{Removal or Storage Requirement}

The developments at this consolidation have their waste collected from the curbside and because DSNY does not pick up from the curb everyday there is a high likelihood that this site is not in compliance as they cannot store waste in an exterior compactor on days when DSNY cannot pick up. 

Kraus Management (MB 1) reported at the time of the survey that DSNY comes three days a week. The consolidation also reported that it does not receive bulk tickets. In terms of storage, some residents of this consolidation have access to trash chutes. Residents of the developments that do not drop their waste at drop-sites on the premises. Most tenants dispose of their trash outside of their building. Once waste is collected from the grounds, waste is stored on the curbside or next to the building depending on the building. 

The consolidation reported that, on average, fewer than 100 compactor bags (40 lbs. bags) are disposed of from Kraus Management (MB 1) daily. There are seven interior compactors, which are all accessible. 

According to the survey, there are no external sources of trash and bulk waste illegally dumped at this site. Ms. Lemon reports that an exterminator comes once a month to deal with any pest issues. 

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Kraus Management (MB 1)  an A rating. 