
\textbf{Inspection and Collection Requirement}

The consolidation appeared to be in compliance with the inspection and collection requirements of Paragraph 45 of the HUD agreement. Compliance could not conduct a site visit during the 2019-2020 period; however, in a phone interview conducted in the summer of 2020, the consolidation reported the following conditions.)

The Property Manager, Damien White, reported that Queensbridge North does not always have enough staff to correct observed deficiencies and caretakers cannot usually complete all of their tasks in a day. NYCHA caretakers pick up trash inside the buildings multiple times a day, including weekends. NYCHA caretakers also conduct ground inspections and pick up litter multiple times a day, including weekends. Staff begins collecting trash at 6:00 AM and ends at 7:00 PM daily. 

\textbf{Removal or Storage Requirement}

The consolidation appeared to be in compliance with the  removal or storage requirement of Paragraph  45 of the HUD Agreement because it has containers in the form of exterior compactors to store waste in a manner that prevents pests on the days DSNY does not come to pick up waste. Based on the same summer of  2020 survey, the consolidation reported the following conditions.

Queensbridge North reported at the time of the survey that DSNY comes five times a week. The consolidation also reported that it received eight bulk tickets a month for the removal of bulk waste.  Bulk trash sits in a yard with an exterior container before being picked up by the vendor. In terms of storage, residents of this consolidation have access to trash chutes and may drop their waste at 12 additional sites on the premises. Tenants are asked by management to leave their garbage on development grounds if they are unable or choose not to use the chutes. Most tenants dispose of their trash in front of their buildings. Once waste is collected from the grounds, waste is stored in an exterior compactor. 

The consolidation reported that, on average,100-200 compactor bags (40 lbs. bags) are disposed of from Queensbridge North daily. There are three exterior compactors at this consolidation and two 30-yard bulk containers. Mr. White also reported that there are 47 interior compactors, which are all accessible.

According to the survey, there are occasionally external sources of trash and bulk waste illegally dumped at this site from outside contractors. Mr. White reports that there is a significant amount of trash at this consolidation and more staff is needed to supplement the AWS system.

3. \textbf{Additional Context} 

In a June 24, 2020 report, the Monitor Cleanliness Team gave Queensbridge North an A- rating. 