The Harlem River consolidation is located in Harlem, Manhattan. This consolidation is comprised of six developments: Audubon Houses, Bethune Gardens, Harlem River Houses, Harlem River II Houses, Marshall Plaza, and Washington Heights Rehab Phase III. Harlem River Houses is bordered by West 151st and West 153rd, Macombs Place and the Harlem River Drive. It is a federally funded conventional development that finished construction in 1937 and is one of the first two original housing projects in New York City. It is made up of seven residential buildings that range between 4 to 5-stories. The buildings cover 7.39 acres in which there are 564 apartments officially housing 1,077 people. \par \vspace{.7\baselineskip}Harlem River II Houses is bordered by West 152nd and West 151st, Douglass Boulevard and Macombs Place. It is a federally funded conventional development that finished construction in 1965. It is a single 15-story building. The building covers 0.66 acres in which there are 116 apartments officially housing 285 people. \par \vspace{.7\baselineskip}Audubon Houses, named after John James Audubon, is bounded by Amsterdam Avenue and West 154th and West 155th Streets. It is a federally funded conventional development that finished construction in 1962. It is a single 20-story building. The building covers 0.63 acres in which there are 166 apartments officially housing 460 people. \par \vspace{.7\baselineskip}Bethune Gardens, named after Mary McLeod Bethune, is bordered by West 156th Street, and St. Nicholas and Amsterdam Avenues. It is a federally funded conventional development that finished construction in 1967. It is a single 22-story building that exclusively houses seniors. The building covers 1.46 acres in which there are 206 apartments officially housing 205 people.\par \vspace{.7\baselineskip}Marshall Plaza, named after Thurgood Marshall, is between Broadway, Amsterdam Avenue, and West 157th and West 158th Streets. It is a federally funded turnkey development that was acquired by NYCHA in 1986. It is a single 13-story building that exclusively houses seniors. The building covers .46 acres in which there are 175 apartments officially housing 211 people.\par \vspace{.7\baselineskip}Washington Heights Rehab Phase III is located between West 156th, West 164th and West 165th Streets, Broadway and Amsterdam Avenue. It is a federally funded turnkey development that was acquired by NYCHA in 1987. It is made up of eight 5-story buildings. The building covers 0.67 acres in which there are 14 apartments officially housing 30 people.