Forest Consolidation Overview

Located in the Morrisania neighborhood of The Bronx, the Forest Consolidation comprises three developments: Forest Houses, McKinley Houses and Eagle Avenue -- East 163rd Street. All developments were all created under federal programs. Staff are deployed from a management office in Forest Houses. Built in 1956, the Forest Houses are located between Tinton Avenue and Trinity Avenue east to west and between E 166th Street and E 163rd Street north to south. The property is a conventional development. Forest Houses is made up of fifteen 9, 10 and 14-story residential buildings covering 17.72 acres. There are 1,326 households with an official population of 2,908 residents. The property has multiple recycling bins and three exterior compactors.

The McKinley Houses, named after President William McKinley, are located on Tinton Street between E 161st Street and E 163rd Street. The property is a conventional development and finished construction in 1962. The McKinley Houses is made up of five 16-story residential buildings covering 6.66 acres. There are 605 households with an official population of 1,387 residents. The property has multiple recycling bins and two exterior compactors. 

Eagle Avenue -- East 163rd Street is located on Eagle Street between E 161st Street and E 163st Street. The property is a turnkey development and finished construction in 1971. The development is one 6-story residential building covering 0.65 acres. There are 62 households with an official population of 127 residents. There is one recycling bin and no exterior compactors on the development while trash is brought to compactors at other developments within the consolidation. 