The Throggs Neck Consolidation consists of three developments located in the Throggs Neck neighborhood of The Bronx. The Throggs Neck Houses are bordered by Randall, Calhoun, Sampson and Balcom Avenues. This conventional development was part of a federal program and finished construction in 1953. Throggs Neck Houses consists of 29 buildings, three and seven stories tall on a 32.83 acre site. There are 1,165 households with an official population of 2,603. There are multiple recycling bins and five exterior compactors for waste storage.\par \vspace{.7\baselineskip}The Throggs Neck Addition is adjacent to the Throggs Neck Houses and borders Dewey, Balcolm and Randall Avenues. This conventional development was part of a federal program and finished construction in 1971. The Addition consists of four buildings, 8 and 11-stories tall on an 8.84 acre site. There are 280 households with an official population of 669. There are multiple recycling bins on site, while waste is transported to the Throggs Neck Houses for storage.\par \vspace{.7\baselineskip}The Randal Aveenue-Balcolm Avenue development is bordered by Randall, Balcolm, Schley and Buttrick Avenues.  This turnkey development was part of a federal program that finished construction in 1978. The development consists of three buildings that are six stories tall and deisgned for seniors exclusively. There are 245 households with an official population of 276. There are multiple recycling bins on the site and one exterior compactor for waste storage.