Douglass Overview:    

  

The Douglass Consolidation is located in Manhattan. This consolidation is named after Fredrick Douglass and is comprised of four developments: Douglass I, Douglass II, Douglass Addition, and 830 Amsterdam Avenue. Douglass I is located between West 100th and West 104th Streets, from Manhattan to Columbus Avenues. It is a federally funded conventional development that finished construction in 1958. It is made up of eleven residential buildings that are either 5, 9, 12, 17 or 20- stories tall. The buildings cover 12.24 acres in which there are 1,297 apartments officially housing 2,630 people.     



Douglass II is located between West 100th and West 104th Streets, from Amsterdam to Columbus Avenues. It is a federally funded conventional development that finished construction in 1958. It is made up of six residential buildings that are either 9, 12, 17, 18 or 20- stories tall. The buildings cover 9.53 acres in which there are 746 apartments officially housing 1,583 people.     

    

Douglass Addition is located on Amsterdam Avenue between West 102nd and West 103rd Streets . It is a federally funded conventional development that finished construction in 1965. It is a single 16-story building. The building covers 0.55 acres in which there are 133 apartments officially housing 335 people.     

 

830 Amsterdam Avenue is located on Amsterdam Avenue between West 100th and West 101st Streets . It is a federally funded conventional development that finished construction in 1965. It is a single 20-story building. The building covers 0.66 acres in which there are 156 apartments officially housing 346 people.