The Baisley Park consolidation is a diverse, sprawling set of developments located in Jamaica, Queens and its surrounding neighborhoods. \par \vspace{.7\baselineskip}Baisley Park \par \vspace{.7\baselineskip}Built in 1961, Baisley Park is a 7.48-acre, 386-unit federally-funded conventional development. This site consists of 5 residential buildings, 3 playgrounds, and a community center. The official population is 927. \par \vspace{.7\baselineskip}Conlon Life Tower \par \vspace{.7\baselineskip}Built in 1973, Conlon Life Tower is a 1.19-acre single-building turnkey development for seniors. This site is also federally funded and has 13 stories. Its official population is 238 and Conlon Life has 216 units. \par \vspace{.7\baselineskip}The FHA Repossessed Group are a series of foreclosed homes which were transferred to NYCHA by HUD between the 1960s and 1980s. They are scattered across the Jamaica section of Queens and its surrounding neighborhoods, such as Springfield Gardens and St. Albans. These are all federally-funded, conventional developments. \par \vspace{.7\baselineskip}Group I consists of 25 1-2 story homes transferred to NYCHA in 1969. This development has 32 units in total and spans across 2.5 acres. The official population is 27. \par \vspace{.7\baselineskip}Group II consists of 12 1-3 story homes transferred to NYCHA in 1970. The 1.63-acre development has 17 units and an official population of 22. \par \vspace{.7\baselineskip}Group III consists of 11 1-2 story homes transferred to NYCHA in 1971. The 1.11-acre development has 15 units and an official population of 18. \par \vspace{.7\baselineskip}Group IV consists of 13 1-3 story homes transferred to NYCHA in 1971. The 1.37-acre development has 15 units and an official population of 20. \par \vspace{.7\baselineskip}Group IX consists of 16 1-2 $\frac{1}{2}$ story homes transferred to NYCHA in 1983. The 1.16-acre development has 41 units and an official population of 31. \par \vspace{.7\baselineskip}Group V consists of 31 1-3 story homes transferred to NYCHA in 1972. The 3.24-acre development has 38 units and an official population of 60. \par \vspace{.7\baselineskip}Group VI consists of 7 1-2 $\frac{1}{2}$ story homes transferred to NYCHA in 1976. The 1.07-acre development has 9 units and an official population of 11. \par \vspace{.7\baselineskip}Group VII consists of 8 1-2 $\frac{1}{2}$ story homes transferred to NYCHA in 1976. The 0.94-acre development has 10 units and an official population of 8.\par \vspace{.7\baselineskip}Group VIII consists of 9 1-2 $\frac{1}{2}$ story homes transferred to NYCHA in 1976. The 0.8-acre development has 11 units and an official population of 13. \par \vspace{.7\baselineskip}Group X consists of 20 1-2 $\frac{1}{2}$ story homes transferred to NYCHA in 1983. The 2.29-acre development has 20 units and an official population of 34.\par \vspace{.7\baselineskip}International Tower is a federally-funded single residential building for seniors acquired by NYCHA in 1983. The development has 10 stories and spans across 0.98 acres. It has 159 units and an official population of 179.\par \vspace{.7\baselineskip}Shelton House is a federally funded conventional development built in 1978. It is a single residential building also for seniors, spanning across 0.5 acres. The development has 12 stories, and has an official population of 165 with 155 units.