:     

   

The Gompers Consolidation is located in the Lower East Side of Manhattan. This consolidation is named after Samuel Gompers and is comprised of six developments: Gompers Houses, 45 Allen Street, Hernandez Apartments, Lower East Side I Infill, Meltzer Tower, and Seward Park Extension. Gompers Houses is located between Delancey, Pitt and Stanton Streets. It is a federally funded conventional development that finished construction in 1964. It is made up of two residential buildings that are 20- stories tall and two non-residential buildings. The buildings cover 3.7 acres in which there are 470 apartments officially housing 1,058 people. 

45 Allen Street is bordered by Grand, Allen, Hester and Eldridge Streets. It is a federally funded turnkey development that finished construction in 1974. It is made up of a single 14-story residential building and one non-residential building. The buildings cover 0.91 acres in which there are 103 apartments officially housing 230 people. 

Hernandez Apartments is named after is Rafael Hernandez. It is bordered by Allen, Stanton, Eldridge, and East Houston Streets. It is a federally funded conventional development that finished construction in 1971. It is a single 17- story residential building. The building covers 1.03 acres in which there are 149 apartments officially housing 259 people. 

Lower East Side I Infill is bordered by Delancey, Rivington, Forsythe and Eldridge Streets. It is a federally funded turnkey development that finished construction in 1988. It is made up of five residential buildings that are 4 and 9- stories tall. The buildings cover 1.98 acres in which there are 189 apartments officially housing 362 people. 

Meltzer Tower is named after Max M. Meltzer. It is located between East 1st and East 2nd Streets, First Avenue and Avenue A. It is a federally funded conventional development that finished construction in 1971. It is a single 20-story building exclusively for seniors. The building covers 1.15 acres in which there are 227 apartments officially housing 251 people. 

Seward Park Extension is bordered by Broome, Norfolk, Grand and Essex Streets. It is a federally funded conventional development that finished construction in 1973. It is made up of two residential buildings that are 23- stories tall and two non-residential buildings. The buildings cover 2.08 acres in which there are 354 apartments officially housing 796 people. 