Wise Towers Consolidation Overview

The Wise Towers Consolidation consists of eight developments in the Upper West Side neighborhood of Manhattan. The Wise Towers, named for Stephen S. Wise, are located between West 90th and West 91st Streets, and Columbus and Amsterdam Avenues. This conventional development came out of a mixed finance/LLC1 program and finished construction in 1965. Wise Towers consists of two, 19-story buildings on a 2.3 acre site. There are 387 households with an official population of 736 residents. 

The De Hostos Apartments, named after Eugenio Maria de Hostos, are bordered by Amsterdam Avenue, Broadway, and West 93rd and West 94th Streets. This conventional development came out of a federal program and finished construction in 1969. De Hostos Apartments consists of a single 22-story building on a .75 acre site. There are 217 households with an official population of 460 residents.

The Wise Rehab development is bordered by Columbus Avenue, Central Park West, and West 93rd and West 94th Streets. This conventional development came out of a federal program and completed rehabilitation in 1964. Wise Rehab consists of a single five-story building on a 0.23 acre site. There are 40 households with an official population of 69 residents.

The Thomas Apartments, named after activist Sondra Thomas, is bordered by West 90th and 91st Streets and Amsterdam and Columbus Avenues. This turnkey development came out of a federal program and completed construction in 1994. Thomas Apartment consists of a single 11-story building on a 0.22 acre site. There are 86 households with an official population of 96 residents. 

The final four developments come out of the West Side Urban Renewal (WSUR) project. The WSUR Brownstones are bordered by West 89th, West 90th, West 91st, and West 93rd Streets, Columbus Avenue and Central Park West. This conventional development came out of a federal project and was completed in 1968. There are 36 brownstone buildings, three, four and six stories tall. The 1.55 acre site has 233 households and an official population of 337 residents. 

The WSUR (Site A) 120 West 94th Street development is located on West 94th Street between Amsterdam and Columbus Avenues. This conventional development came out of a federal project and was completed in 1965. Site A consists of a single 9-story building on a 0.52 acre site. There are 69 households with an official population of 145 residents.

The WSUR (Site B) 74 West 92nd Street development is located on West 92nd Street between Columbus Avenue and Central Park West. This conventional development came out of a federal project and was completed in 1965. Site B consists of a single 22-story building on a 0.58 acre site. There are 166 households with an official population of 328 residents. 

The WSUR (Site C) 589 Amsterdam Avenue development is located on Amsterdam Avenue between West 88th and West 89th Streets. This conventional development came out of a federal project and was completed in 1965. Site C consists of a single 18-story building on a 0.58 acre site. There are 155 households with an official population of 342 residents.

Waste at all sites is collected from the curbside by DSNY.