Carey Gardens Consolidation Overview

The Carey Gardens consolidation consists of three developments located in the Coney Island neighborhood of Brooklyn. Carey Gardens, named after former NYCHA Chairperson Gerald J. Carey, lies between Surf and Neptune Avenues, running from West 22nd to West 24th Streets. This conventional development came out of a federal program and finished construction in 1970. Carey Gardens consists of three buildings, 15 and 17-stories tall. The 8.37 acre site has 666 households with an official population of 1,585 residents. There are recycling bins on site and two exterior compactors for waste storage.

Coney Island I (Site 1B) is bordered by West 35th and 36th Streets, and Surf and Mermaid Avenues. This turnkey development came out of a federal program and was completed in 1973. Site 1B consists of a single 14-story building on a 1.41 acre site. The development has 189 households with an official population of 488 residents. There are recycling bins on site and waste is brought to Carey Gardens for storage.

The Haber Houses, named for State Assemblyperson Bernard Haber, is bordered by West 24th and West 25th Streets, Surf Avenue and Riegelmann Boardwalk. This conventional development came out of a federal program and finished construction in 1965. Haber Houses consists of three, 14-story buildings on a 3.09 acre site. Designed exclusively for seniors, the development has 378 households with an official population of 448. There are recycling bins on site and waste is brought to the curbside for collection by DSNY.