Jackie Robinson Consolidation Overview

The Jackie Robinson Consolidation consists of five developments located in the East Harlem neighborhood of Manhattan. The Robinson Houses, named after baseball player Jackie Robinson, are located between East 128th and East 129th Streets, and Lexington and Park Avenues. This turnkey development came out of a federal program and finished construction in 1973. Robinson Houses consists of a single eight-story building on a 1.49 acre site. There are 186 households with an official population of 415 residents. Trash is brought to the UPACA (Site 6) development for storage. 

The Morris Park Senior Citizens Home is located on East 124th Street between Madison and Fifth Avenues. This conventional development came out of a federal program and finished construction in 1977. The senior citizens home is a 9-story building on a .23 acre site. There are 95 households with an official population of 104. Trash is brought to the UPACA (Site 6) development for storage.

The Park Avenue-East 122nd Street, 123rd Streets is located between East 122nd and East 123rd Streets, and Park and Lexington Avenues. This turnkey development came out of a federal program and finished construction in 1970. The development consists of two, six-story buildings on a .74 acre site. There are 88 households with a total population of 209 residents. Trash is brought to the UPACA (Site 6) development for storage.

The final two developments are named after the Upper Park Avenue Community Association (UPACA). The UPACA (Site 5) development is bordered by East 120th and East 121st Streets and Lexington and Park Avenues. This turnkey development came out of a federal program and finished construction in 1986. Site 5 consists of a single 11-story building for seniors only. The 1.46 acre site has 176 households with an official population of 206 residents. Trash is brought to the UPACA (Site 6) development for storage.

The UPACA (Site 6) development is bordered by East 119th and East 122nd Streets and Park and Lexington Avenues. This turnkey development came out of a federal program and finished construction in 1987. Site 6 consists of a single 12-story building for seniors only. The 1.04 acre site has 147 households and an official population of 178 residents. There are two exterior compactors for waste storage.