Unity Plaza Consolidation Overview

The Unity Plaza Consolidation consists of four developments in the East New York neighborhood of Brooklyn. Fiorentino Plaza is bordered by Wyona Street, and Glenmore, Van Siclen and Pitkin Avenues. This conventional development came out of a federal program and finished construction in 1971. Fiorentino Plaza consists of eight, four-story buildings on a 2.18 acre site. There are 154 households with an official population of 438 residents. 

Long Island Baptists Houses is bordered by Hinsdale Street, and Sutter, Sheffield and Dumont Avenues. This conventional development came out of a federal program and finished construction in 1981. Long Island Baptists Houses consists of four, six-story buildings on a 1.81 acre site. There are 223 households with an official population of 522 residents.

Unity Plaza (Sites 17, 24 and 25A) is bordered by Sutter, Blake, Sheffield and Alabama Avenues. This turnkey development came out of a federal program and was completed in 1973. Sites 17, 24 and 25A are three buildings, six stories each on a 1.85 acre site. There are 166 households with an official population of 463 residents.

Unity Plaza (Sites 4-27) is between Blake and Hinsdale Streets, and Sheffield and Dumont Avenues. This conventional development came out of a federal program and was completed in 1973. Sites 4-27 consist of five, six-story buildings on a 5.72 acre site. There are 456 households with an official population of 1,123 residents.

Waste is placed on the curbside for collection by DSNY for all developments.