The Claremont Consolidation consists of seven developments in the Claremont neighborhood of The Bronx. The 1162-1176 Washington Avenue consolidation is bordered by East 167th and East 168th Streets and Third and Washington Avenues. This turnkey development came out of a federal program and finished construction in 1975. The development consists of a single six-story building on a 0.44 acre site. There are 64 households with an official population of 167. Waste is brought to the Teller Avenue-East 166th Street development for storage.\par \vspace{.7\baselineskip}Claremont Rehab (Group 2) is bordered by Clay and Webster Avenues, and East 166th and East 169th Streets. This turnkey development came out of a federal program and finished rehabilitation in 1987. Group 2 consists of six buildings, five and six-stories tall. The 0.73 acre site has 104 households with an official population of 240 residents. Waste is brought to the College Avenue-East 165th Street and the Teller Avenue-East 166th Street developments for storage.\par \vspace{.7\baselineskip}Claremont Rehab (Group 3) is bordered by Teller and Findlay Avenues, and East 165th and East 167th Streets. This turnkey development came out of a federal program and finished rehabilitation in 1985. Group 3 consists of five, five-story buildings on a 0.81 acre site. There are 104 households with an official population of 244 residents. Waste is brought to the College Avenue-East 165th Street and the Teller Avenue-East 166th Street developments for storage.\par \vspace{.7\baselineskip}Claremont Rehab (Group 4) is bordered by East 165th and 169th Streets, and Clay and Findlay Avenues. This turnkey development came out of a federal program and finished rehabilitation in 1986. Group 4 consists of nine buildings, four and five-stories tall. The 1.04 are site has 144 households with an official population of 322 residents. Waste is brought to the College Avenue-East 165th Street and the Teller Avenue-East 166th Street developments for storage.\par \vspace{.7\baselineskip}Claremont Rehab (Group 5) is bordered by East 166th and East 167th Streets, and Findlay and College Avenues. This turnkey development came out of a federal program and finished rehabilitation in 1985. Group 5 consists of three, five-story buildings on a 1.24 acre site. There are 125 households with an official population of 292 residents. Waste is brought to the College Avenue-East 165th Street and the Teller Avenue-East 166th Street developments for storage.\par \vspace{.7\baselineskip}The College Avenue-East 165th Street development is bordered by East 165th and East 166th Avenues and Findlay and College Avenues. This turnkey development came out of a federal program and finished construction in 1972. The development consists of a single six--story building on a 0.51 acre site. Built exclusively for seniors, there are 93 households with an official population of 101 residents. There is one exterior compactor for waste storage.\par \vspace{.7\baselineskip}The Teller Avenue-East 166th Street development is bordered by Teller and Clay Avenues and East 166th and East 167th Streets. This turnkey development came out of a federal program and finished construction in 1971. The development consist of a single six-story building on a 0.63 acre site. There are 88 households with an official population of 183 residents. There is one exterior compactor for waste storage.