

The Fort Washington Avenue Rehab Consolidation consist of five developments in the Washington Heights neighborhood of Manhattan. The Fort Washington Ave Rehab development is located between West 163rd and West 165th Streets, Fort Washington Avenue to Riverside Drive. This federal turnkey development came out of federal program and finished rehabilitation in 1985. The development consists of a single seven-story building on a 2.57 acre site. Design exclusively for seniors, the building has 226 households with an official population of 275.

Washington Heights Rehab (Groups 1\& 2) is located between West 176th and West 177th Streets, and Amsterdam and Audubon Avenues. This conventional development came out of a federal program and finished rehabilitation in 1988. Groups 1\&2 consist of a five buildings, five and six-stories tall. The 1.32 acre site has 213 households with an official population of 405 residents.

Washington Heights Rehab Phase III (Fort Washington) is between West 156th, West 164th and West 165th Streets, Broadway and Amsterdam Avenue. This turnkey development came out of a federal program and finished rehabilitation in 1987. The development consists of eight, five-story buildings on a 0.67 acre site. There are 87 households with an official population of 176 residents.

Washington Heights Rehab IV ( C) is between West 175th and West 177th Streets, Amsterdam and Audubon Avenues. This conventional development came out of a federal program and finished construction in 1990. The development consists of two, five-story buildings on a 0.2 acre site. There are 32 households with an official population of 67 residents.

Washington Heights Rehab IV (D) is on West 176th Streets, between Amsterdam and Audubon Avenues. This conventional development came out of a federal program and finished construction in 1990. The development consists of two, five-story buildings on a 0.2 acre site. There are 31 households with an official population of 60 residents.

Waste is placed on the curbside for collection by DSNY for all developments.