

The Lower East Side Consolidation consists of five developments located in the Lower East Side neighborhood of Manhattan. Bracetti Plaza, named after Mariana Bracetti, is located between East 3rd  and East 4th Streets, between Avenues B and C. This turnkey development came out of a federal program and finished construction in 1974. Bracetti Plaza consists of a single seven-story building on a 1.02 acre site. There are 108 households with an official population of 252 residents. Trash is collected from the curbside by DSNY.

Campos Plaza II, named after Pedro Albizu Campos, is bordered by East 14th and East 13th Streets, from Avenue B to Avenue C. This conventional development came out of a federal program and finished construction in 1983. Campos Plaza II consists of two buildings, 9 and 17-stories tall. The 2.14 acre site has 223 households and an official population of 505 residents. Waste is brought to the Riis Houses development for storage. 

First Houses, named for being the first public housing development in the city, is located between East 2nd and East 3rd Streets, Avenue A and First Avenue. This conventional development also came out of a federal program and finished construction in 1936. First Houses consists of eight, four and five-story buildings on a 1.23 acre site. The development has 123 households with an official population of 182 residents. Trash is collected from the curbside by DSNY.

Lower East Side II is bordered by East 4th, East 5th and East 6th Streets, and Avenues B, C and D. This turnkey development came out of a federal program and finished construction in 1988. The development consists of four, three-story buildings on 3.85 acres. There are 185 households with an official population of 422 residents. Trash is collected from the curbside by DSNY.

Lower East Side Rehab (Group 5) is bordered by East 6th and 7th Streets and Avenue C. This turnkey development came out of a federal program and completed rehabilitation in 1986. Group 5 consists of two six-story buildings on a 0.41 acre site. There are 54 households with an official population of 117 residents. Trash is collected from the curbside by DSNY.