The Union Avenue Consolidation consists of six developments spanning over a large section of the South Bronx. Claremont Parkway-Franklin Avenue is bordered by Claremont Parkway, East 171st Street, and Fulton and Third Avenues. This turnkey development came out of a federal program and was completed in 1986. The development consists of three buildings, three and seven-stories tall. The 3.09 acre site has 185 households with an official population of 272 residents. Waste is brought to the adjacent Union Avenue-East 166th Street development for storage.\par \vspace{.7\baselineskip}Davidson Houses, named after community leader Lewis S. Davidson Sr., is located between Prospect and Union Avenues, and Home and East 167th Streets. This conventional development came out of a federal program and was completed in 1973. Davidson Houses consists of a single eight-story building on a 1.9 acre site. There are 172 households with an official population of 466 residents. There is one exterior compactor for waste storage.\par \vspace{.7\baselineskip}South Bronx Area (Site 402) is bordered by East 158th and 161st Streets and Cauldwell and Eagle Avenues. This turnkey development came out of a federal program and was completed in 1988. Site 402 consists of four, three-story buildings on a 3.43 acre site. There are 110 households with an official population of 372 residents. Waste is brought to Claremont Parkway-Franklin Avenue or Davidson Houses for storage. \par \vspace{.7\baselineskip}Stebbins Avenue-Hewitt Place is bordered by Hewitt Place, Dawson Street, and Westchester and Rev. Polite Avenues. This turnkey development came out of a federal program and was completed in 1987. The development consists of two, three-story buildings on a 2.83 acre. There are 118 households with an official population of 265 residents. Waste is brought to Claremont Parkway-Franklin Avenue or Davidson Houses for storage.\par \vspace{.7\baselineskip}Union Avenue-East 163rd Street is between East 163rd and East 165th Streets, and Prospect and Union Avenues. This turnkey development also came out of a federal program and was completed in 1985. The development consists of a single nine-story building on a 2.65 acre site. Built exclusively for seniors, there are 195 households with an official population of 230 residents. Waste is brought to Claremont Parkway-Franklin Avenue or Davidson Houses for storage.\par \vspace{.7\baselineskip}Union Avenue-East 166th Street is bordered by East 166th and Home Streets, and Prospect and Union Avenues. This turnkey development also came out of a federal program and was completed in 1988. The development consists of six, three-story buildings on a 2.27 acre site. There are 118 households with an official population of 277 residents. There is one exterior compactor for waste storage.