Kraus Management (MB 1) Consolidation Overview

The Kraus Management (MB 1) Consolidation consists of eight developments scattered throughout the borough of Manhattan. The 154 West 84th Street development is located on 84th Street between Amsterdam and Columbus Avenues in the Upper West Side. This turnkey development came out of a federal program and was completed in 1996. The development consists of a single seven-story building on a 0.92 acre site. There are 35 households with an official population of 71 residents. 

Lower East Side III is bordered by East 8th and 9th Streets and Avenues C and D in the Lower East Side. This turnkey development also came out of a federal program and was completed in 1997. The development consists of two, four-story buildings on a 0.98 acre site. There are 56 households with an official population of 171 residents.

The Rehab Program (Douglas Rehabs) development, named after Frederick Douglas, is bordered by West 101st and West 104th Streets, Broadway and West End Avenue in the Upper West Side. This conventional development came out of a federal program and finished rehabilitation in 1964. The Douglas Rehabs consist of four buildings three, six and seven-stories tall. Covering 0.56 acres, the development has 112 households with an official population of 176 residents. 

The Rehab Program (Taft Rehabs) development, named for Senator Robert A. Taft, is bordered by St. Nicholas and Lenox Avenues and West 112th and West 119th Streets in Harlem. This conventional development also came out of a federal program and finished rehabilitation in 1961. The Taft Rehabs consists of three, seven-story buildings over 0.62 acres. There are 151 households with an official population of 276 residents.

The following three developments come out of the Multifamily Home Ownership Program (MHOP) and are named after councilmember Frederick E. Samuel. The program was created to give eligible families the opportunity to purchase an apartment in a limited equity co-op and eventually sell the property to the residents. Samuel (MHOP) I is bordered by West 139th and West 141st Streets, Adam Clayton Powell Boulevard and Lenox Avenue in Harlem. Samuel I consists of five, five-story buildings on a 0.32 acre site. Completed in 1994, there are 28 residents with an official population of 49 residents. 

Samuel (MHOP) II is bordered by West 139th Street, Adam Clayton Powell Boulevard and Lenox Avenue in Harlem. Samuel II consists of a single five-story building on a 0.07 acre site. Completed in 1993, there are four house holds with an official population of 12 residents.

Samuel (MHOP) III is bordered by West 142nd Street, Adam Clayton Powell Boulevard and Lenox Avenue in Harlem. Samuel III consist of a single five-story building  on a 0.12 acre site. Completed in 1995, there are two households with an official population of three residents.

The Stanton Street development is bordered by Attorney, Stanton and Ridge Streets in the Lower East Side. The turnkey development came out of a federal program and was completed in 2003. Stanton Street consists of a single three-story building on a 0.11 acre site. There are 13 households with an official population of 34 residents.

Waste is placed on the curbside for collection by DSNY for all developments. 