Building Management Associates (BX 1)\par \vspace{.7\baselineskip}The Building Management Associates (BX 1) Consolidation consists of eight developments located in the southeast of The Bronx. Bryant Avenue-East 174th Street is bordered by East 173rd and East 174th Streets, and Bryant and Vyse Avenues. This turnkey development came out of a federal program and finished construction in 1972. The development consists of a single six-story development on a 0.52 acre site. There are 72 households with an official population of 139 residents.\par \vspace{.7\baselineskip}East 165th Street-Bryant Avenue is bordered by Westchester, Longfellow and Hoe Avenues and Aldus Street. This turnkey development came out of a federal program and finished construction in 1987. The development consists of five, three-story buildings on a 3.16 acre site. There are 110 households with an official population of 361 residents. \par \vspace{.7\baselineskip}East 173rd Street-Vyse Avenue is bordered by Southern Boulevard, East 173rd and Jennings Streets, and Vyse Avenue. This turnkey development also came out of a federal program and finished construction in 1987. The development consists of seven, three-story buildings on a 4.5 acre site. There are 162 households with an official population of 381 residents.\par \vspace{.7\baselineskip}Hoe Avenue- East 173rd Street is bordered by Hoe and Vyse Avenues, and East 173rd and East 174th Streets. This turnkey development came out of a federal program and finished construction in 1970. The development consists of a single six-story building on a 0.51 acre site. There are 65 households with an official population of 146 residents.\par \vspace{.7\baselineskip}Hunts Point Rehab is bordered by Lafayette, Hunts Point, and Seneca Avenues, and Irvine Street. This turnkey development came out of a federal program and finished rehabilitation in 1991. Hunts Point Rehab consists of 12, 4 and 5-story buildings on a 1.34 acre site. There are 130 households with an official population of 320 residents. \par \vspace{.7\baselineskip}Longfellow Avenue Rehab is bordered by East 165th Street, and Whitlock, Westchester and Bryant Avenues. This turnkey development came out of a federal program and finished rehabilitation in 1990. The development consists of two, five-story buildings on a 0.61 acre site. There are 75 households with an official population of 273 residents. \par \vspace{.7\baselineskip}West Farms Road Rehab is bordered by Jennings and Freeman Streets, West Farms Road, and Longfellow Avenue. This turnkey development came out of a federal program and finished rehabilitation in 1986. The development consists of four, six-story buildings on a 1.19 acre site. There are 208 households with an official population of 442 residents.\par \vspace{.7\baselineskip}West Farms Square Conventional is bordered by East 167th Street, Longfellow Avenue and West Farms Road. This conventional development came out of a federal program and finished construction in 1994. The development consists of a single five-story building on a 0.11 acre site. There are 20 households with an official population of 47 residents.\par \vspace{.7\baselineskip}Waste is placed on the curbside for collection by DSNY for all developments.